---
title: "SWC Final Exercise"
author: "Breanna Pasko"
date: "April 19, 2015"
output: html_document
---

This is my final exercise for the Software Carpentry workshop. I have chose Brazil, Djibouti, and Oman as my countries of interest.


```{r,message=FALSE, echo=F}
library("dplyr")
```

```{r, echo=FALSE}

gap.in<- read.table("~/Desktop/swc_arlington/Sunday_scripts/output/combined_gapMinder.tsv", sep = "\t", header = TRUE)
gap.in %>%
  filter(country == "Brazil") -> Brazil
gap.in %>%
  filter(country == "Djibouti") -> Djibouti
gap.in %>%
  filter(country == "Oman") -> Oman
plot(x=Brazil$year,y=Brazil$gdpPercap,main="Brazil",xlab="year",ylab="GDP")
plot(x=Djibouti$year,y=Djibouti$gdpPercap,main="Djibouti",xlab="year",ylab="GDP")
plot(x=Oman$year,y=Oman$gdpPercap,main="Oman",xlab="year",ylab="GDP")
```

**Brazil:**
Mean = `r mean(Brazil$lifeExp)`
Max = `r max(Brazil$lifeExp)`
Min = `r min(Brazil$lifeExp)`

**Djibouti:**
Mean = `r mean(Djibouti$lifeExp)`
Max = `r max(Djibouti$lifeExp)`
Min = `r min(Djibouti$lifeExp)`

**Oman:**
Mean = `r mean(Oman$lifeExp)`
Max = `r max(Oman$lifeExp)`
Min = `r min(Oman$lifeExp)`
```{r}


```

```{r, echo=FALSE}

#Default bin widths
hist(gap.in$lifeExp,main="Global Life Expectancy",xlab="Life Expectancy")

#Narrower bin widths
hist(gap.in$lifeExp,main="Global Life Expectancy",xlab="Life Expectancy",breaks=50)
```

The average global life expectancy is around 70 years old!